\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\geometry{
  top=1.8cm,
  bottom=2.2cm,
  left=2cm,
  right=2cm
}
\title{Documentation for Channel Class}
\author{Project: Fairness in WiFi and 5G Coexistence}
\date{}

\begin{document}

\maketitle

\section{Channel Class Documentation}
\label{sec:channel}

The \texttt{Channel} class is a core component of the wireless coexistence simulator, representing a multi-band wireless medium. It handles signal propagation, capacity constraints, and ongoing transmission state across different frequency bands.

\subsection*{Attributes}
\begin{itemize}
  \item \textbf{env}: The SimPy simulation environment controlling time and events.
  \item \textbf{bands}: A tuple defining the frequency bands available (e.g., 2.4GHz, 5GHz, 6GHz).
  \item \textbf{tx\_power\_dBm}: Transmit power of the sender node in decibels-milliwatts (default = 20).
  \item \textbf{pathloss\_exponent}: Exponent used for modeling free-space signal decay (default = 3.0).
  \item \textbf{noise\_floor\_dBm}: Ambient background noise level (default = -95 dBm).
  \item \textbf{rx\_sensitivity\_dBm}: Minimum signal strength required for successful reception (default = -82 dBm).
  \item \textbf{max\_capacity}: Maximum allowed channel usage per simulation second (1.0 represents full utilization).
  \item \textbf{used\_capacity}: Tracks how much of the channel is currently being used.
  \item \textbf{transmissions}: Dictionary mapping each band to its list of ongoing transmissions (each as a tuple of transmitter and end time).
\end{itemize}

\subsection*{Constructor}
\begin{lstlisting}[language=Python]
def __init__(self,
             env: simpy.Environment,
             bands=('2.4GHz', '5GHz', '6GHz'),
             tx_power_dBm=20,
             pathloss_exponent=3.0,
             noise_floor_dBm=-95,
             rx_sensitivity_dBm=-82):
\end{lstlisting}

\begin{itemize}
  \item Initializes a channel object with configurable radio characteristics.
  \item Prepares an internal registry for each band to track ongoing transmissions.
\end{itemize}

\subsection*{Purpose in Project}
This class is essential to simulate real-world behavior of wireless media in a coexistence environment. It enables:

\begin{itemize}
  \item Simulating interference and collisions across multiple radios (Wi-Fi vs. 5G NR-U).
  \item Estimating whether a message can be received based on signal strength and interference.
  \item Supporting Cellular Automata rules by giving feedback on signal conditions.
\end{itemize}


The \texttt{Channel} object models the local view of the medium required for CA-based decentralized decision-making.

\end{document}
